\section{}
Consider the general form of momentum balance
\begin{align}
    \rho \frac{dv_i}{dt} = \frac{\partial T_{ji}}{\partial x_j} + \rho b_i \label{eq:1}
\end{align}
where d/dt is the total derivative; $v_i$ is the velocity; 
$\rho$ denotes density; $T_{ij}$ is the stress tensor and $b_i$ is a body force. 
This equation says that inertial and body forces are balanced by the gradients of the stress tensor.

The general form of the stress tensor reads
\begin{align}
    T_{ij} = -p \delta_{ij} + \mu \left(\frac{\partial v_i}{\partial x_j} + 
    \frac{\partial v_j}{\partial x_i} \right) - \frac{2}{3} \mu 
    \frac{\partial v_k}{\partial x_k} \delta_{ij} + \kappa \left(
    \frac{\partial v_k}{\partial x_k} \delta_{ij} \right) \label{eq:2}
\end{align}
where $p$ is the pressure, $\mu$ is the shear (dynamic) viscosity and $\kappa$ is the 
dialation viscocity. For each question assume the viscosities $\mu$ and $\kappa$ are constant.

\begin{enumerate}[label=(\alph*)]
    \item Using equations (1) and (2) derive the general form of Navier-Stokes equations for
    compressible viscous fluid. Note: only index notation can be used. The final form of
    equations should be presented in operator (vector) form.
    \item Assuming $\kappa = 0$, write the full set of Navier-Stokes equations
    in Cartesian coordinates assuming two-dimensional flow (two equations corresponding to $x$ and $y$
    directions).
\end{enumerate}

\subsection*{Solution}
\subsection{}
First, deal with the stress tensor.
\begin{align*}
    T_{ji} = -p \delta_{ji} + \mu \left(\frac{\partial v_j}{\partial x_i} +
    \frac{\partial v_i}{\partial x_j} \right) - \frac{2}{3} \mu
    \frac{\partial v_k}{\partial x_k} \delta_{ji} + \kappa \left(
    \frac{\partial v_k}{\partial x_k} \delta_{ji} \right)
\end{align*}
Differentiate with respect to $x_j$,
\begin{align*}
    \frac{\partial T_{ji}}{\partial x_j} &= -\frac{\partial p}{\partial x_j} \delta_{ji}
    + \mu \left(\frac{\partial^2 v_j}{\partial x_j \partial x_i} + 
    \frac{\partial^2 v_i}{\partial x_j^2} - 
    \frac{2}{3} \frac{\partial^2 v_k}{\partial x_j \partial x_k} \delta_{ji}\right) + 
    \kappa \left(\frac{\partial^2 v_k}{\partial x_j \partial x_k} \delta_{ji} \right)  
\end{align*}
Substituting into equation \ref{eq:1},
\begin{align*}
    \rho \frac{dv_i}{dt} &= -\frac{\partial p}{\partial x_j} \delta_{ji}
    + \mu \left(\frac{\partial^2 v_j}{\partial x_j \partial x_i} + 
    \frac{\partial^2 v_i}{\partial x_j^2} - 
    \frac{2}{3} \frac{\partial^2 v_k}{\partial x_j \partial x_k} \delta_{ji}\right) + 
    \kappa \left(\frac{\partial^2 v_k}{\partial x_j \partial x_k} \delta_{ji} \right) + \rho b_i \\
    \rho \frac{dv_i}{dt} &= -\partial_{j}
\end{align*}


